Single-step Hybrid Predition

### 2017-03-14 reports/methods.Rmd
Methods: Kernels and LOOCV

### Kernels

@@

### Leave-one-out cross-validation (LOOCV)

>>>>

### Kernels
BLUP models are computationally attractive when the number of features $p$
exceeds the number of genotypes $n$ and are equivalent to a selection index
when fixed effect have been accomodated by the dependent variable
(@Mrode2014, pp. 34, 311, 312).
Depending on the data set, up to three predictors were available for agronomic
trait predictions, namely pedigree data (P), genomic data (G) and
transcriptompic data (T).
The corresponding feature matrix of the $l$-th group of inbred lines and the 
$o$-th predictor ($\mathbf{W_{lo}}$) has dimensions $n \times p$ where $n$
pertains to the number of gneotypes in the $l$-th group and $p$ pertains to 
the number of features.
For the diversity panel maize lines, $n$ corresponds to the number of genotypes
whereas, in the case of the hybrid data, $n$ corresponds to the number of
parent lines in the corresponding heterotic group.
In generating kernels for each predictor, all features in $\mathbf{W_{lo}}$ were
centered and standardized to unit variance.
Then, each kernel can be defined as

$$
\begin{equation} \label{eq:GenomicRelationship}
  \mathbf{G}_{lo} = \frac{1}{W_{lo}} \mathbf{W}_{lo} \mathbf{W}_{lo}^{\top},
\end{equation}
$$
where $W$ denotes the number of features [@VanRaden2008].
In the case of pedigree data (P), coancestry coefficients were used directly
for $\mathbf{G}_{lo}$.

@@

### Leave-one-out cross-validation
In the case of the diversity panel maize inbred lines, leave-one-out cross
validation (LOOCV) was done by simply using a single genotype as a hold-out
sample, which will subsequently be predicted, while using all other inbred 
lines for model training.
This process is repeated until all inbred lines have been used once for testing
and $n - 1$ times for model training.

For the hybrid data, LOOCV was carried out as follows:
Let $D$ and $F$ denote the set of parental inbred lines from the Dent and the 
Flint group, respectively.
Further, let $H \cap [D \times F]$ denote the set of hybrids from crosses 
between $D$ and $F$.
The training set ($H_{TRN}$) for the hybrid to be predicted ($H_{ij}$) --- 
where $i \in D_{TRN}$ and $j \in F_{TRN}$ --- was assembled as 
$H_{TRN} = [H \cap (D_{TRN}^{C} \times F_{TRN}^{C})]$, where 
$D_{TRN}^{C} = D \setminus D_{TRN}$ and $F_{TRN}^{C} = F \setminus F_{TRN}$.
